Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-04 paper/ms.tex
Make ack in alpha order
Fix reference to appendix

\subsection{Quantification} \label{ssec:quant}
First, we illustrate the time-dependence of one possible inaccurate reference
frame. Throughout this work we will consider three orbits typical of the
stellar thin disk, stellar thick disk, and the stellar halo. We summarize
their initial position in phase space and the actions of their integrated
orbits in Table~\ref{tab:orbits}. Each orbit is plotted in \Gus{Appendix X}.
We will refer to these orbits by their names henceforth.

@@

\acknowledgments
We would like to thank David W. Hogg, Kathryn Johnston, and Megan Bedell for
many useful discussions. A.B. would like to thank Todd Phillips for helpful
discussions. A.B. was supported in part by the Roy \& Diana Vagelos Program in
the Molecular Life Sciences and the Roy \& Diana Vagelos Challenge Award. The
work of \Gus{everyone} is supported by the Simons Foundation.

>>>>

\subsection{Quantification} \label{ssec:quant}
First, we illustrate the time-dependence of one possible inaccurate reference
frame. Throughout this work we will consider three orbits typical of the
stellar thin disk, stellar thick disk, and the stellar halo. We summarize
their initial position in phase space and the actions of their integrated
orbits in Table~\ref{tab:orbits}. Each orbit is plotted in
Appendix~\ref{app:orbits}. We will refer to these orbits by their names
henceforth.

@@

\acknowledgments
We would like to thank Megan Bedell, David W. Hogg, and Kathryn Johnston for
many useful discussions. A.B. would like to thank Todd Phillips for helpful
discussions. A.B. was supported in part by the Roy \& Diana Vagelos Program in
the Molecular Life Sciences and the Roy \& Diana Vagelos Challenge Award. The
work of \Gus{everyone} is supported by the Simons Foundation.
